---
title: "hw_wk1"
author: "Yunting Chiu"
date: "8/28/2020"
output: pdf_document
---

## The Code of question 3a to 3d
#### Libraies and read Data

```{r}
library(readr)
library(tidyverse)
library(ggplot2)
library(mosaic)
SDE <- read_csv(file = "../data/case0102.csv")
tail(SDE)
```


3.	Using R find numerical and graphical summaries of this data. Use these to describe the distribution of the starting salaries for both males and females.

a.	Give and interpret the mean salary and standard deviation of salaries for females. Do this also for males.
```{r}
#mean salary of female and male
SDE %>%
  filter(Sex == "Female") -> SDE_Female
mean(SDE_Female$Salary)  
SDE %>%
  filter(Sex == "Male") -> SDE_Male
mean(SDE_Male$Salary)

# SD
sd(SDE_Female$Salary)  #SD for Female
sd(SDE_Male$Salary) # SD for Male
```

b.	Give and interpret the median salary and the IQR of salaries for females. Do this also for males.
```{r}
# find interquartile range of female in R
summary(SDE_Female$Salary)  

# find interquartile range of male in R
summary(SDE_Female$Salary)  
```

c.	Give a histogram of salaries for each group. 
```{r}
hist(SDE_Female$Salary)
hist(SDE_Male$Salary)
```

d.	Give side-by-side boxplots of salaries.
```{r}
SDE %>%
  ggplot(mapping = aes(x = Sex, y = Salary, fill = Sex))+
  geom_boxplot()+
  theme_bw()
```

e. Use a. to d. to describe the distribution of salaries for each group.
```{r}
favstats(Salary ~ Sex, data = SDE)
histogram(~Salary | Sex, data = SDE, col = "red")
```



