---
title: "HW7"
author: "Yunting Chiu"
date: "11/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(mosaic)
fev <- read_csv("FEV.csv")
fev
```

-  Smoking status (0 = non-smoker/1 = current smoker).
```{r}
fev %>%
  mutate(logFEV = log(FEV)) -> fev02
fev02 %>%
  mutate(Smoke = recode(Smoke, "0" = "non-smoker",
                               "1" = "current_smoker")) -> fev
fev
```

```{r}
favstats(logFEV ~ Smoke, data = fev)
```

```{r}
qplot(x = fev$Smoke, y = fev$logFEV, geom = "boxplot",
      fill = I("dark green"),color = I("black"))
```
- qq
```{r}
# qqplots/Quantile-Quanitle Plots/Normal Scores plots
qplot(sample = logFEV, facets = . ~ Smoke, data = fev, geom = "qq") + geom_qq_line()
# formal test of normality in each group
shapiro.test(fev$logFEV[fev$Smoke == "non-smoker"])  
shapiro.test(fev$logFEV[fev$Smoke == "current_smoker"])

```

```{r}
# two-sample t-procedure
t.test(logFEV ~ Smoke, data = fev, conf.level = 0.95) # two-sided test
t.test(logFEV ~ Smoke, data = fev, conf.level = 0.95, var.equal = T) # two-sided test
```

- SLR
1.  Smaller residuals are better
2.  If it isn’t significant, then the coefficient really isn’t adding anything to the model and could be dropped or investigated further.  Pr(>|t|) is the significance level.
3. Residual Standard Error: This is the standard deviation of the residuals.  Smaller is better.
4. Multiple / Adjusted R-Square(bigger is better) : For one variable, the distinction doesn’t really matter.  R-squared shows the amount of variance explained by the model.  Adjusted R-Square takes into account the number of variables and is most useful for multiple-regression.
5. F-Statistic: The F-test checks if at least one variable’s weight is significantly different than zero.  This is a global test to help asses a model. If the p-value is not significant (e.g. greater than 0.05) than your model is essentially not doing anything.
- Reference: http://www.learnbymarketing.com/tutorials/linear-regression-in-r/
```{r}
reg.out <- lm(logFEV ~ Smoke, data = fev02)
reg.out
anova(reg.out)
summary(reg.out)
# logFEV = 0.8884 + 0.2721*smoke
```

```{r}
# plots the data and the fitted regression line using ggplot
fev02 %>%
ggplot(aes(x = Smoke, y = logFEV)) + 
  geom_point()+
  geom_smooth(method=lm,se=F) +
  ggtitle("Smoke group vs. log FEV with fitted LSR line")
```

```{r}
# check assumptions
par(mfrow=c(2,2))
qqnorm(reg.out$residuals,pch=19)
qqline(reg.out$residuals)
hist(reg.out$residuals)
plot(reg.out$fitted.values,reg.out$residuals,pch=19,main='Residuals vs. fitted values')
plot(fev02$Smoke, reg.out$residuals, pch=19, main='Residuals vs. Smoke')
```

